---
title: "DECLARATION OF PROTECTIVE COVENANTS, CONDITIONS AND RESTRICTIONS FOR GLENLAKE SUBDIVISION, PHASE NO. 1 PLAT BOOK 157, PAGE 250"
output: pdf_document
---

|                                                                                                                                                                                                                                                                                                                                                                                                                                |
|--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
| **Disclaimer**: this document is a transcription of the original deed, registered at the Spartanburg Register of Deeds in deed book 82R, page 862, and serve only to provide a searchable form on the declaration. This document cannot be used to claim legal standing. This document has been compiled from the original Declaration and the subsequent Amendments 1, 2, 3 and 4 and some of the Supplementary Declarations. |

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

BINDING ARBITRATION
This is the First page of the Covenants, Conditions and Restrictions for Glenlake Subdivision. Pursuant to South Carolina Code Section 15-48-10 et seq., as amended. these Covenants, Conditions and Restrictions are subject to the following:

THESE COVENANTS, CONDITIONS AND RESTRICTIONS ARE SUBJECT TO ARBITRATION UNDER ARTICLE XVII HEREIN. THESE COVENANTS, CONDITIONS AND RESTRICTIONS ARE BINDING ON ALL OWNERS OF LOTS WITHIN GLENLAKE SUBDIVISION, PHASE NO. 1 AND SUBSEQUENTLY INCORPORATED PHASES. INCLUDING ANY PERSON OBTAINING FINANCIAL RIGHTS IN SAID LOTS.

This Declaration imposes assessments constituting a lien on each Lot in the Subdivision. Please contact the Association to determine the status of a particular Lot with regard to payment of assessments.

In the event other pages, including, but not limited to, cover pages, indexes, or tables of contents, are placed in front of this page, those pages shall not be deemed the first page. This page and only this page shall be deemed or considered the first page of the Covenants, Conditions and Restrictions for all legal purposes.

\newpage

\tableofcontents

\newpage

## DECLARATION OF PROTECTIVE COVENANTS, CONDITIONS AND RESTRICTIONS FOR GLENLAKE SUBDIVISION, PHASE NO. 1 PLAT BOOK 157, PAGE 250 

THIS DECLARATION is made on this the \_\_\_ day of March, 2005 by Four Bees, Inc., a South Carolina corporation, (herein referred to sometimes as "Four Bees" and sometimes as "Declarant") and Poinsett Homes, LLC, a South Carolina limited liability company, (herein referred to sometimes as "Poinsett Homes").


```{r child='section00.Rmd'}

```

```{r child='section01.Rmd'}

```

```{r child='section02.Rmd'}

```

```{r child='section03.Rmd'}

```

```{r child='section04.Rmd'}

```

```{r child='section05.Rmd'}

```

```{r child='section06.Rmd'}

```

```{r child='section07.Rmd'}

```

```{r child='section08.Rmd'}

```

```{r child='section09.Rmd'}

```

```{r child='section10-11.Rmd'}

```

```{r child='section12.Rmd'}

```

```{r child='section13.Rmd'}

```

```{r child='section14.Rmd'}

```

```{r child='section15.Rmd'}

```

```{r child='section16-18.Rmd'}

```
