---
title: "DECLARATION OF PROTECTIVE COVENANTS, CONDITIONS AND RESTRICTIONS FOR GLENLAKE SUBDIVISION, PHASE NO. 1 PLAT BOOK 157, PAGE 250"
output: pdf_document
---

**Disclaimer**: this document is a transcription of the original deed, registered at the Spartanburg Register of Deeds in deed book xxx, page yyy, and serve only to provide a searchable form on the declaration. This document cannot be used to claim legal standing.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

THIS DECLARATION is made on this the ___ day of March, 2005 by Four
Bees, Inc., a South Carolina corporation, (herein referred to sometimes as "Four Bees" and sometimes as
"Declarant") and Poinsett Homes, LLC, a South Carolina limited liability company, (herein referred to
sometimes as "Poinsett Homes").

```{r child='section00.Rmd'}

```

```{r child='section01.Rmd'}

```

```{r child='section02.Rmd'}

```

```{r child='section03.Rmd'}

```

```{r child='section04.Rmd'}

```

```{r child='section05.Rmd'}

```

```{r child='section06.Rmd'}

```

```{r child='section07.Rmd'}

```

```{r child='section08.Rmd'}

```


```{r child='section15-17.Rmd'}

```