---
title: "Organization of the Annual Meeting and Board elections"
output: 'pdf_document'
bibliography: ../bibliography/biblio.json
csl: ../bibliography/acs.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
library(knitr)
library(lubridate)

TOTALHOMES = 482

```

```{r functions, include=FALSE}
yearstext <- function(t, num_years = 3) {

    this_year <- lubridate::year(lubridate::today())

    evenyears <- this_year  + this_year %% 2 + 2 * 0:(num_years - 1)
    oddyears <- evenyears - 1

    if (t == "odd") {
        return(paste0(trimws(paste(oddyears, collapse = ", ")), ", etc."))
    }
    else if (t == "even") {
        return(paste0(trimws(paste(evenyears, collapse = ", ")), ", etc."))
    }
    else return("")
  }

```


>Author: Rob Hanssen

>Version: `r format(lubridate::today(), format="%B %d, %Y")`

# Purpose

Organizing the elections of the Board of Directors and the Annual Meeting are essential parts of the function of the Board of Directors. Elections take place every year at the Annual Meeting. This guideline offers a time line to organize the elections and the Annual Meeting in an efficient manner.

\tableofcontents
\newpage


# Background

## History

During the first election after the developer handover in 2018, seven Directors were elected in accordance with the Bylaws,[@by0303]^,^[@by0305b] four of those with a term of two years and three with a term of one year. All directors elected after the first election will have a two-year term.[@by0305b] Because of the staggering of terms, during the odd years (*e.g.* `r yearstext("odd")`), three positions are available and during the even years (*e.g.* `r yearstext("even")`), four positions are available. In accordance with the Bylaws, one position on the Board of Directors must be filled by a representative of the Town Home owners.[@by0305c]

## Vacancies

Positions that are vacant due to resignation of a Director need to be filled by a vote of the Board of Directors if the term of the vacant position is not due during the elections, however the Board can choose to elicit input in filling the position using the ballot. This will not change the length of the term of the position.[@by0307]

## Candidate qualifications

The qualifications for the nominees are:[@by0301]^,^[@cov0511c]

1.  An owner of a home within Glen Lake in good standing
2.  Residing in the neighborhood
3.  Not be a spouse of a board member

*Good standing* is defined as having paid all annual assessments and fines[@cov0511c]^,^[@by0306] and having no suspension of voting rights for any reason.[@cov0511c]^,^[@cov142a3] *Owner of a home* is defined as being listed on the deed or be the spouse of the person listed on the deed.[@by0301]^,^[@cov0402]^,^[@cov01owner]


## The Nomination Committee

The Nomination Committee is authorized in the Bylaws[@by0304] and created by the Board of Directors via a resolution.[@res2018012] The task of the Nomination Committee is to organize the election process, the Town Hall meetings, the Annual Meeting and the Organizational Meeting. During this process, several letters need to be sent out to the homeowners with approval of the Board of Directors; a location for the Annual Meeting needs to be found, approved by the Board and booked; a location for the Town Halls (typically the Glen Lake Club House) needs to be booked. To facilitate communication to the homeowners, signs can be printed, and social media can be used.

# Guidelines for the timing of specific actions and events:

## Early-October: Assemble the Nominations Committee

Volunteers are appointed to the Nominations Committee.

## Early to Mid-December: Send nomination letter to all HOA members

This letter serves as the request for nominations to run for the Board. Typically, the term for the return of nominations is 2 to 4 weeks. The Christmas and New Year's vacation will cause delays in the return and all care should be taken to have the nomination letters in the member's home before December 4^th^. This letter can also be used to request questions that can be used at the Town Hall meetings. The last function of this letter can be to announce the date of the Annual Meeting, however the Annual Meeting can officially only be announced up to 60 days before the date of the Annual Meeting.[@by0204] The best opportunity to send this letter is to add it to the budget package sent out mid-November to limit the expense.

For convenience and speed, the nomination form and town hall questions form can also be made available on the Association website. During the 2019 elections, all nominations and most questions came in via the website.

See Appendix 1 for an example letter and nomination form.

## Mid-December: Secure the location to be used for the Annual Meeting

For all elections since 2020 the Glen Lake Club House was used at no cost.  Alternatively, in 2018 and 2019, the lunchroom of Boiling Springs Elementary School was used to host the Annual Meeting and Elections (the cost was approximately \$150). Other locations can also be used. The location should be able to host 50 people and should have a PA system.

## Mid-January: Send ballot and accompanying letter to all HOA members

This letter serves as the final announcement for the Annual Meeting and will describe the voting process. The letter is typically sent, so that receipt of the ballot coincides with the nomination town halls, however the latest this announcement can be sent is 10 days before the Annual Meeting.[@by0204] The letter and ballot should reference the quorum needed to validate the election (25% of the Total Association Vote; `r TOTALHOMES %/% 4` ballots).[@by0209]^,^[@by0211]

See Appendix 2 for an example letter and Appendix 3 for an example ballot form.

## Mid-January: Nomination town halls

Typically, two town hall meetings are held where nominees for the Board can answer questions from HOA members. These questions can come from the audience or from pre-selected questions determined by the Nomination Committee or otherwise. Depending on the size of the group of nominees, there can be anywhere from 5 to 10 questions with answer times from 2 to 5 minutes. To increase participation of the homeowners, at least one meeting should be scheduled on a weekend day.

## Mid-January: Announce the possibility of granting proxies

Homeowners can also grant other HOA members a proxy to attend the Annual Meeting and vote on their behalf. All proxies shall be in writing, dated, and filed with the Secretary before the appointed time of each meeting. Every proxy is revocable and will automatically cease when the proxied member's lot is sold or when the proxied member is present at the meeting.[@by0208]

An example of a proxy form can be found in Appendix 4.

## Mid-January: Settle on a date for the Organizational Meeting

All Directors and nominees must agree on the date for the Organizational meeting which will be held within 10 days of the Annual Meeting and Board of Director elections. It is prudent to have a date available for all potential Directors so that the Organizational Meeting can take place in accordance with the Bylaws.[@by0308] The Organizational Meeting can be announced on the website calendar.

## Mid-January: Organize the vote counters

The counting of the votes should be done by neutral parties, *i.e.* homeowners with no ties to the nominees or third-party civic organizations, such as the Beta Club, Scouts organizations, fraternities or sororities, etc. If the Nomination Committee decides to use third parties, these should be notified to participate. During most elections, the Social Committee has volunteered as vote counters.

## Mid-January: Arrange the presence of a recording secretary **(OPTIONAL)**

To capture all information communicated from and to the homeowners during the Annual Meeting, it is possible to use a third-party professional recording secretary. The management company has a list of people who can function as such. This person will need to be booked for the event.

## Two weeks before the Annual Meeting

Determine if all the candidates are still eligible to enter the elections. All candidates must have a zero-balance with the Association and adhere to all other requirements.[@by0301]^,^[@cov0511c]^,^[@cov142a3] The board can expel board members by a simple majority vote if they are delinquent for 30 days or more.[@by0306] Because the due date for the annual assessment is January 1^st^, membera who did not pay by February 1^st^ are delinquent.

## One week before the Annual Meeting and Elections

Determine if the quorum for the Annual Meeting has been met (25% of the Total Association Vote,[@by0209] approximately `r TOTALHOMES %/% 4` votes or proxies). If the quorum has not been reached, start a (social media or other) campaign to ensure that the quorum is made before or at the Annual Meeting. This is not an uncommon occurrence -- in the elections of 2018 through 2022, the quorum was reached during the week before the meeting after significant posting on social media and using signs at the entrances.

It is advisable to add a statement on the ballot letter and the ballot that states that the ballot is a proxy for presence at the meeting to make sure that the quorum can be reached with ballots alone.

## Early to mid-February: Annual Meeting and Special Meeting for the election of the Board of Directors

The Annual Meeting must take place within 60 days from the end of the previous fiscal year.[@by0202] The latest that the meeting can take place is February 29^th^ during leap years and March 1^st^ during regular years. To increase participation from the homeowners, the Annual Meeting is best scheduled on a weekend day, however it is best to avoid Superbowl weekend. From the end of the previous fiscal year until the day of the election, the board members will hold office until their successors are elected.[@by0305b]

The agenda for the Annual Meeting must at least include the following items. Other items are optional.

1.  Opening by the President of the Board of Directors
2.  Confirmation of the quorum (attendees, ballots, proxies)
3.  Call for nominations from the floor; Casting of votes; Motion to close the votes and commence with counting of the votes.
4.  Treasury report by the Treasurer
5.  Open forum
6.  Report of the results of the elections

*Ad 2.* If the quorum of the meeting is not met, the meeting cannot proceed and must be adjourned to a meeting between 5 and 30 days later.[@by0206] Because Association funds will need to be spent on setting up a new meeting and announcing it to the homeowners, it is of the utmost importance that the quorum is met before or at the original meeting.

*Ad 3.* Nominations from the floor during the meeting is prescribed in the Bylaws[@by0304] and must be called for. If there is a nomination from the floor, the nominee must be given the opportunity to present themselves to the audience. During the 2018 and 2019 elections, no one was nominated in this fashion, and in 2020 one person was nominated from the floor. The consequence of calling nominations from the floor is that homeowners need to be able to change their ballots to accommodate voting for the new nominees. New ballots will need to be available during the meeting with blank spots for floor nominees.

*Ad 4.* The Annual Treasury report must be reviewed at the Annual Meeting in a manner the Board of Directors can decide.[@cov1512]

*Ad 5.* The Open Forum is done in a manner the Board of Directors can decide.

*Ad 6.* If there is a quorum, the nominees with the highest vote counts will be elected to the Board of Directors. The results of the vote count must be in the minutes of the meeting[@by0211] together with the quorum requirement. One position on the Board of Directors must be filled by a representative of the Town Homes who must also be on the Town Home Committee.[@by0305c] If no representative of the Town Homes has enough votes to be elected to the Board, they will still be appointed to the Board and replace the person on the Board who had the lowest vote count.

The first meeting of the newly elected Board members must take place within 10 days of the election and is called the Organizational Meeting.[@by0308]

## Mid-February: Organizational Meeting

The Board of Directors meets in a public meeting to elect the officers (President, Vice President, Treasurer, Secretary) and handle the transition of information to the newly elected Board members. The method to elect Officers can be decided by the Directors. The length of the term remaining to the Director is of no consequence to their ability to be elected as Officer.

It is best to use this meeting to set the meeting schedule for the rest of the year and communicate this schedule via regular mail. This meeting should also include an executive session to transfer privacy-sensitive information to the newly elected Board members.

# Regular Meetings

There must be at least one meeting per quarter,[@by0309] *i.e.* four meetings per year. If there are no deviations from the schedule set during the Organizational Meeting and communicated via regular mail, no further notice is required.[@by0309] For convenience, the meetings can be announced on the Association website. During regular meetings, a majority of the Board members needs to be present to conduct any business.[@by0312]

\newpage
```{r child = 'appendix01.Rmd'}
```

\newpage
```{r child = 'nominationform.Rmd'}
```


\newpage
```{r child = 'appendix02.Rmd'}
```


```{r child = 'appendix03.Rmd'}
```

\newpage
```{r child = 'appendix04.Rmd'}
```


\newpage
# References
